\bf Supplement to ``On Devon Allen's Disqualification at the 2022 World Track and Field Championships''

### 2024-11-30 Manuscript/supp.tex
Updated some small stuff and left a comment

As an alternative to the methods described in Section 3.1 of the main paper, it
is possible to combine all men's and women's reaction time (RT) data for each of 
the three competition
comparisons.  Thus we shrink our analyses from six to three, but each analysis
is roughly twice as big as previously.  For the 2019 versus 2022 comparison,
there were 258 RTs from 65 athletes and the asymptotic
test result was a p-value of $3.56 \cdot 10^{-8}$. For the 2022 national versus
international comparison, there were 160 RTs from 35
athletes and the asymptotic test result was a p-value of $1.94 \cdot 10^{-7}$.
For the 2023 versus 2022 comparison, there were 343 RTs
from 92 athletes and the asymptotic test result was a p-value of
$4.99 \cdot 10^{-12}$.  These are all highly significant test results that show
substantial differences in average RT for athletes competing at
multiple championship-level events.

@@

\jy{Men's data or pooled data?}
\eds{with or without 2022?}

>>>>

As an alternative to the methods described in Section 3.1 of the main paper, it
is possible to combine all men's and women's reaction time (RT) data for each of 
the three competition
comparisons.  Thus we shrink our analyses from six to three, but each analysis
is roughly twice as big as previously.  For the 2019 versus 2022 comparison,
there were 258 RTs from 65 athletes and the asymptotic
test result was a p-value of $3.56 \cdot 10^{-8}$. For the 2022 national versus
international comparison, there were 160 RTs from 35
athletes and the asymptotic test result was a p-value of $1.94 \cdot 10^{-7}$.
For the 2023 versus 2022 comparison, there were 343 RTs
from 92 athletes and the asymptotic test result was a p-value of
$4.99 \cdot 10^{-12}$.  As a result of the larger sample sizes, the code was
very computationally expensive to run and thus we ran it on a smaller size.  All
three permutation tests had a p-value of $1 \cdot 10^{-5}$, which is the smallest
possible value given the permutation test size of $100,000$.  When taken together
with the asymptotic results, the results becoems very clear. These are all
highly significant test results that show substantial differences in average RT
for athletes competing at multiple championship-level events.

@@

\jy{Men's data or pooled data?}
\eds{with or without 2022?}
\of{I dont know if we have time for this or if this fits the scope of what we
are working on.}
